Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-07-07 outputs/paper/paper.qmd
Update paper.qmd

pollu_temp %>% filter(pollutant != "CO" & pollutant != "SO2" & 
  (month_name == "Dec" | month_name == "Jan"| month_name == "Feb" | 
  month_name == "Mar")) %>% ggplot(aes(max_temp, mean_pollution, 
  color=month_name)) + geom_point() + facet_grid(. ~ pollutant) + 
  labs(color="Month") + xlab("Maximum Temperature") + 
  ylab("Mean Pollution")
```

@@

pollu_temp %>% filter((pollutant == "CO" | pollutant == "SO2") & 
  (month_name == "Dec" | month_name == "Jan"| month_name == "Feb" | 
  month_name == "Mar")) %>% ggplot(aes(max_temp, mean_pollution, 
  color=month_name)) + geom_point() + facet_grid(. ~ pollutant) + 
  labs(color="Month") + xlab("Maximum Temperature") + 
  ylab("Mean Pollution")

@@

pollu_temp %>% filter(pollutant != "CO" & pollutant != "SO2" & 
  (month_name == "Apr" | month_name == "May" | month_name == "Jun" | 
  month_name == "Jul")) %>% ggplot(aes(max_temp, mean_pollution, 
  color=month_name)) + geom_point() + facet_grid(. ~ pollutant) + 
  labs(color="Month") + xlab("Maximum Temperature") + 
  ylab("Mean Pollution")

@@

pollu_temp %>% filter((pollutant == "CO" | pollutant == "SO2") & (month_name == "Apr" |
   month_name == "May" | month_name == "Jun" | month_name == "Jul")) %>% ggplot(aes(max_temp,
   mean_pollution, color=month_name)) + geom_point() + facet_grid(. ~ pollutant) + 
  labs(color="Month") + xlab("Maximum Temperature") + 
  ylab("Mean Pollution")

@@

pollu_temp %>% filter(pollutant != "CO" & pollutant != "SO2" & (month_name == "Aug" | 
    month_name == "Sep" | month_name == "Oct" | month_name == "Nov")) %>% ggplot(aes(max_temp,
    mean_pollution, color=month_name)) + geom_point() + facet_grid(. ~ pollutant) + 
    labs(color="Month") + xlab("Maximum Temperature") + ylab("Mean Pollution")

@@

pollu_temp %>% filter((pollutant == "CO" | pollutant == "SO2") & 
  (month_name == "Aug" | month_name == "Sep" | month_name == "Oct" | month_name == "Nov")) %>%
  ggplot(aes(max_temp, mean_pollution, color=month_name)) + geom_point() + facet_grid(. ~
  pollutant) + labs(color="Month") + xlab("Maximum Temperature") + ylab("Mean Pollution")

>>>>

pollu_temp %>% filter(pollutant != "CO" & pollutant != "SO2" & (month_name == "Dec" | month_name == "Jan"| month_name == "Feb" | month_name == "Mar")) %>% ggplot(aes(max_temp, mean_pollution, color=factor(month_name, level=level_order))) + geom_point() + facet_grid(. ~ pollutant) + labs(color="Month") + xlab("Maximum Temperature") +  ylab("Mean Pollution")
```

@@

pollu_temp %>% filter((pollutant == "CO" | pollutant == "SO2") & (month_name == "Dec" | month_name == "Jan"| month_name == "Feb" | month_name == "Mar")) %>% ggplot(aes(max_temp, mean_pollution, color=factor(month_name, level=level_order))) + geom_point() + facet_grid(. ~ pollutant) + labs(color="Month") + xlab("Maximum Temperature") +  ylab("Mean Pollution")

@@

pollu_temp %>% filter(pollutant != "CO" & pollutant != "SO2" & (month_name == "Apr" | month_name == "May" | month_name == "Jun" |  month_name == "Jul")) %>% ggplot(aes(max_temp, mean_pollution, color=factor(month_name, level=level_order))) + geom_point() + facet_grid(. ~ pollutant) + labs(color="Month") + xlab("Maximum Temperature") + ylab("Mean Pollution")

@@

pollu_temp %>% filter((pollutant == "CO" | pollutant == "SO2") & (month_name == "Apr" |month_name == "May" | month_name == "Jun" | month_name == "Jul")) %>% ggplot(aes(max_temp, mean_pollution, color=factor(month_name, level=level_order))) + geom_point() + facet_grid(. ~ pollutant) + labs(color="Month") + xlab("Maximum Temperature") +  ylab("Mean Pollution")

@@

pollu_temp %>% filter(pollutant != "CO" & pollutant != "SO2" & (month_name == "Aug" | month_name == "Sep" | month_name == "Oct" | month_name == "Nov")) %>% ggplot(aes(max_temp, mean_pollution, color=factor(month_name, level=level_order))) + geom_point() + facet_grid(. ~ pollutant) + labs(color="Month") + xlab("Maximum Temperature") + ylab("Mean Pollution")

@@

pollu_temp %>% filter((pollutant == "CO" | pollutant == "SO2") & (month_name == "Aug" | month_name == "Sep" | month_name == "Oct" | month_name == "Nov")) %>% ggplot(aes(max_temp, mean_pollution, color=factor(month_name, level=level_order))) + geom_point() + facet_grid(. ~ pollutant) + labs(color="Month") + xlab("Maximum Temperature") + ylab("Mean Pollution")
